What Does Reproducible Research Mean for Plant Pathology?

### 2016-09-06 What Does Reproducible Research Mean for Plant Pathology.Rmd
Add link to r-opensci blog post about R Rsearch Compendiums

### Notes
https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/

>>>>

### Notes
These are links to resources that may be useful for writing this or as suggested resources in the final
document that aren't easily printable for inclusion in the Dropbox folder.

https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/

https://github.com/ropensci/rrrpkg
